Supplemental Information B: Power Simulations

### 2023-06-09 Supplemental-Material-B-Power-Simulation.Rmd
typo

---
title: "Supplemental Information C: Power Simulations"
subtitle: "Supplemental Material for 'Need Fulfillment During Intergroup Contact: Three Experience Sampling Studies'"
author:
- ██████ ██████████^1^
- ██████████ ████████^1^
- █████ █████████^1^
- █████ ██ █████^1^
- ███ ███████^1^
- ^1^██████████ ██ █████████, Department of Psychology
- "Author Information:"
- "Correspondence concerning this article should be addressed to ██████ ██████████, ██████████ ██ ██████████, █████████ ██ ██████████, █████ ██████████ ███, ████ ██ █████████ ████████████████. E-mail: █████████████████"
- 'The main manuscript is available at <a href="https://www.doi.org/ToBePublished" target="_blank">doi.org/ToBePublished</a>'
- 'The data repository for this manuscript is available at <a href="https://osf.io/pr9zs/?view_only=1ea47bb646694632a764dead807ef970" target="_blank">osf.io/pr9zs/?view_only=1ea47bb646694632a764dead807ef970</a>'
- 'The GitHub repository for this manuscript is available at <a href="https://github.com/maskedForPeerReview" target="_blank">github.com/maskedForPeerReview</a>'
date: "Last updated: `r format(Sys.time(), '%d %B, %Y')`"
output: 
  bookdown::html_document2:
    fig_caption: yes
    md_extensions: +footnotes
    code_folding: hide
    mathjax: default
    theme: yeti
    toc: yes
    toc_float: yes
    number_sections: false
    css: style.css
    includes:
      in_header: "_includes/head-custom-rmd.html" 
editor_options:
  chunk_output_type: console
bibliography: references.bib
csl: apa.csl
header-includes:
   - \usepackage{amsmath, nccmath}
---

>>>>

---
title: "Supplemental Information B: Power Simulations"
subtitle: "Supplemental Material for 'Need Fulfillment During Intergroup Contact: Three Experience Sampling Studies'"
author:
- ██████ ██████████^1^
- ██████████ ████████^1^
- █████ █████████^1^
- █████ ██ █████^1^
- ███ ███████^1^
- ^1^██████████ ██ █████████, Department of Psychology
- "Author Information:"
- "Correspondence concerning this article should be addressed to ██████ ██████████, ██████████ ██ ██████████, █████████ ██ ██████████, █████ ██████████ ███, ████ ██ █████████ ████████████████. E-mail: █████████████████"
- 'The main manuscript is available at <a href="https://www.doi.org/ToBePublished" target="_blank">doi.org/ToBePublished</a>'
- 'The data repository for this manuscript is available at <a href="https://osf.io/pr9zs/?view_only=1ea47bb646694632a764dead807ef970" target="_blank">osf.io/pr9zs/?view_only=1ea47bb646694632a764dead807ef970</a>'
- 'The GitHub repository for this manuscript is available at <a href="https://github.com/maskedForPeerReview" target="_blank">github.com/maskedForPeerReview</a>'
date: "Last updated: `r format(Sys.time(), '%d %B, %Y')`"
output: 
  bookdown::html_document2:
    fig_caption: yes
    md_extensions: +footnotes
    code_folding: hide
    mathjax: default
    theme: yeti
    toc: yes
    toc_float: yes
    number_sections: false
    css: style.css
    includes:
      in_header: "_includes/head-custom-rmd.html" 
editor_options:
  chunk_output_type: console
bibliography: references.bib
csl: apa.csl
header-includes:
   - \usepackage{amsmath, nccmath}
---
